Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-26 paper.tex
added the proof of the cumulative budget, will do more edits tomorrow

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. \bccomment{Our current analysis of the cumulative expected payment is wrong. See the comments of Lemma 6 for details}
\label{rst:budget}
\end{theorem}

@@

Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{The proof below only bounds the cumulative expected number of payments}

>>>>

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. 
\label{rst:budget}
\end{theorem}

@@

Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.

\begin{proof}
Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$. Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$. Define
\begin{align}
W^{'}[l] = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n,l), \forall i,t,j\}\nonumber
\end{align}
where $g(n,l)$ is a function which we will define later. Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$. Based on the definition of $W[l]$, we know if $\omega\in W[l]$, the maximum payment we need to offer is bounded above by $R+2Wmg(n,l)$. Thus,

\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\} \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

Set $g(n,l)$ to be $\frac{l}{n}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, we need $n\geq \lceil a_{0} l\rceil$. In order to hvae $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Thus, we know we can only occur regret in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.

Thus,
\begin{align}
\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

Therefore,

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}E[c(t)|\omega_t\in w[l],t\in [t_n,t_{n+1}))P(\omega_t\in w[l],t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega_t\in w[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega_t\in w[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
\end{align}

We now bound $P(\omega\in W[l]|t\in[t_{n},t_{n+1}))$. \bccomment{Is my calculation to bound this probability correct?}
\begin{align}
&P(\omega\in W[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in W^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in W^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(|\epsilon_{i,t}^{j}|<\frac{l}{n}, \forall i,j|t\in[t_n,t_{n+1}))-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right). \label{prob:upper}
\end{align}
Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times. Without loss of generality, we assume it to be arm $1$. Then we know

\begin{align}
\eqref{prob:upper}&\leq P\left(|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-P\left(|\epsilon_{1,t}^{1}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
=&P\left(\frac{l-1}{n}<|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
=&P\left(\frac{\sqrt{n}(l-1)}{n}<|N(0,1)|<\frac{\sqrt{n}l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
=&2\Phi\left(\frac{\sqrt{n}l}{n}\right)-2\Phi\left(\frac{\sqrt{n}(l-1)}{n}\right) \nonumber \\
=&2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}. \nonumber
\end{align}

Thus,
\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
\leq & \sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]\times 2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}Nn. \nonumber \\
\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2n}\right)\sqrt{n}. \nonumber
\end{align}

Denote $k_n=\max\{n_1, \lceil a_0 l \rceil\}$. Then we know
\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}. \nonumber
\end{align}

\begin{lemma}
Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
\end{lemma}
